Recovering from population extinction in the Animal Life Cycle Algorithm (ALCA)

### 2022-10-01 paper.tex
Updated Paper
Work in progress.

    We define extinction as a situation in which something no longer exists; in
    our case scenario, when we refer to extinction in our algorithm, it means
    the population of individuals no longer exists. When this condition
    presents itself, it is required to create a new population to continue
    evolution (restart).

    % Maybe you do it later, but explain what is a restart precisely 
    In a previous work \cite{Felix-Saul2022} we used to generate a new random
    set of solutions, with the cost of losing all evolution knowledge.

    One contribution of this paper is to demonstrate that it is possible to
    evolve a population of individuals, similar to a Genetic Algorithm (GA),
    using a distributed, parallel, and asynchronous methodology by algorithm
    implementation and testing.

>>>>

    We define extinction as a situation in which something no longer exists; in
    our case scenario, when we refer to extinction in our algorithm, it means
    the population of individuals no longer exists. When this condition
    presents itself, it is required to create a new population to continue
    evolution (restart). Population restart is the process in which we create a
    new set of individuals to replace the others that have already died (or
    were discarded) due to their aptitude. In a previous work
    \cite{Felix-Saul2022} we used to generate a new random set of solutions,
    with the cost of losing all evolution knowledge.

    One contribution of this paper is to proof that it is possible to
    evolve a population of individuals, similar to a Genetic Algorithm (GA),
    using a distributed, parallel, and asynchronous methodology by algorithm
    implementation and testing.
